\documentclass{article}
\usepackage[utf8]{inputenc}

\title{journal Wk5-6}
\author{Thomas Kongonis 44618468 }
\date{August 2019}

\begin{document}

\maketitle

\tableofcontents
\vspace{5mm}
\begin{itemize}
\item{Note: All times are in 24hr format.}
\end{itemize}

\section{Miscellaneous}

\date{27/08/2019 12:34}
\begin{itemize}
\item{Intent:Commit documents to Github easier.}


\item{Action:}
\begin{enumerate}
    \item{Reset Github and Overleaf passwords.}
    \item{Link Github to Overleaf.}
\end{enumerate}

\item{Result: Success, although a difficulty I faced was that I needed to reset all of my passwords due to negligence.}
\end{itemize}
\vspace{5mm}

\section{Data Carpentry}

\vspace{5mm}
\section{Elaboration}

\vspace{5mm}

\section{Journal Coding}
\date{27/8/2019 12:52}
\begin{itemize}
\item{Intent: Format Week 5-6 Journal in Overleaf}
\item{Actions:}
\begin{enumerate}
    \item{Created new project and implemented table of contents and sections. Action was successful}
    \item{implemented vspace code to place distance between sections. Action was successful}
    \item{Begun by placing dates before each entry utilising date code. Action was successful}
    \item{Implemented item code within first section. Action was unsuccessful and error message was shown.}
    \item{Followed error instructions and found solution:}
    \subitem{https://www.overleaf.com/learn/latex/Lists}
    \item{Implemented begin item and end item codes. Action was successful.}
    \item{Implemented enumerate code within an itemized list as a formatting choice. Action was successful.}
    \item{Tried to paste link shown above into line 52 and was given a formatting error that stated that my line was too long. Solution used was implementing subitem code beneath item number 5. Action was successful.}
    \end{enumerate}
\item{Results:}
\begin{enumerate}
    \item{I learnt that it is incorrect practice to utilize a code without specifically knowing its purpose as this will cause difficulty.}
    \item{I learnt that the formatting functions of \LaTeX are very useful if the time is taken to implement them correctly.}
    \item{Formatting was successfully implemented after some medium difficulty. Paying attention to the error messages as advised in class and dealing with them as they appear is necessary.}
\end{enumerate}
\end{itemize}


\end{document}
